Batched Bayesian Optimization via Multi-objective Acquisition Function Ensemble for Automated Analog Circuit Design

### 2018-01-30 paper/background.tex
Paper update

@@

We formulate the sizing problem as an optimization problem

\subsection{Gaussian Process}

Basic introduction to GP

\subsection{Acquisition Function}

Introduce LCB, EI and PI

>>>>

% TODO: See how other people describe GP and BO}

@@

% TODO: The circuit performance comes from \bf{circuit} simulation}
% TODO: format, citation of HSPICE/spectre}
% TODO: See how other analog circuit optimization paper formulate the problem}

We handle the scenarios where topology of the analog circuit is fixed, this is
practical as thare are usually a lot of classical topologies for given design
task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is to automatically search for the optimal
design parameters, the problem can then be formulated as a bound-constrained
black-box optimization problem:

\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x})
\end{equation}

where $\bm{x} \in \textrm{D} \subset \textrm{R}^d$ is the design variables
and $f_i(\bm{x})$ represents the $i$-th cared circuit performance like gain
or phase margin of an amplifier. and the $\mathrm{FOM}(\bm{x})$ is the
design objective. Given the design parameters $\bf{x}$, the FOM value can be
obtained via circuit simulation using softwares like HSPICE or spectre.

% TODO: Explain the noise

\subsection{Gaussian Process Regression}

\textcolor{red}{ALERT: COPIED FROM MY PAPER SUMBITTED TO DAC}

We model the $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} with Gaussian
process (GP) model~\cite{GPML}. The GP model is the most commonly used model
for Bayesian optimization, the advantage of GP is that it can give a
well-calibrated uncertainty of prediction. GP is characterized by a mean
function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In this
paper, we use squared-exponential ARD kernel, and a constant mean fucntion
$m(\bm{x}) = \mu_0$ for all our experiments.

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution 
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x}))
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x})
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty.

\subsection{Bayesian Optimization}

Bayesian optimization~\cite{shahriari2016taking} was proposed for the
optimization of expensive black-box functions. It consists of two essential
ingredients, i.e., the probabilistic surrogate models and an acquisition
function. The probabilistic surrogate models provide the prediction with
uncertainties. They are refined incrementally with newly observed data.
Acquisition function is used to explore the state space based on the surrogate
model optimally. The procedure of Bayesian optimization is described in
Algorithm~\ref{alg:BayesianOptAlgo}.

\begin{algorithm}
\caption{Bayesian Optimization}
\label{alg:BayesianOptAlgo}
\begin{algorithmic}[1]
\STATE Initial Sampling
\STATE Construct initial GP model
\FOR{t = 1, 2, \dots}
\STATE Construct the acquisition function
\STATE Find $\bm{x}_t$ that optimizes the acquisition function
\STATE Sample $y_t = f(\bm{x}_t)$
\STATE Update probabilistic surrogate model
\ENDFOR
\STATE Return best $f(\bm{x})$ recorded during iterations
\end{algorithmic}
\end{algorithm}

In Bayesian optimization described in Algorithm~\ref{alg:BayesianOptAlgo}, the acquisition function is used to balance the exploration and exploitation during the optimization. The acquisition fucntion considers both the predictive value and the uncertainty. There are a lot of existing acquisition functions, examples include the lower confidence bound (LCB), expected improvement (EI) and probability of improvement (PI).

The LCB fucntion is defined as follows:
\begin{equation}
    \label{eq:LCB}
\end{equation}
Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP. $\kappa$ is a parameter that balances the exploitation and exploration.

Following the suggestion of~\cite{brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
\begin{equation}
    \label{eq:LCB}
    \begin{array}{lll}
        \kappa &=& \sqrt{\nu \tau_t} \\
        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta)
    \end{array}
\end{equation}
Where $t$ is the number of current iteration. $\nu$ and $\delta$ are two user defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.

### 2018-01-30 paper/intro.tex
Paper update

% TODO: Bayesian optimization is a sequential algorithm, there is a need to
% parallelize it
%
% TODO: cite the two 3D-IC papers of TVLSI
To reduce the circuit simulations needed by the optimization, the Gaussian
process (GP)~\cite{GPML} model has been introduced as online surrogate model to
assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
differential evolution algorithm, in~\cite{lyu2017efficient}. Recently, the
Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been applied for analog circuit
optimization, the Bayesian optimization algorithm is firstly introduced for the
automated design of general analog circuits, and has shown very good
performance compared to other simulation-based approaches,
in~\cite{wang2017efficient}, the Bayesian optimization algorithm is combined
with adaptive Monte-Carlo sampling to optimize the yield of analog circuits and
static random-access memory (SRAM).

>>>>

% TODO: Bayesian optimization is a sequential algorithm, there is a need to
% parallelize it
%
% TODO: cite the two 3D-IC papers of TVLSI
To reduce the number of circuit simulations, the Gaussian process
(GP)~\cite{GPML} model has been introduced as online surrogate model to assist
the optimization. In~\cite{liu2014gaspad}, GP is combined with differential
evolution algorithm, in~\cite{lyu2017efficient}. Recently, the Bayesian
optimization (BO)~\cite{shahriari2016taking} algorithm has been applied for
analog circuit optimization, the Bayesian optimization algorithm is firstly
introduced for the automated design of general analog circuits, and has shown
very good performance compared to other simulation-based approaches,
in~\cite{wang2017efficient}, the Bayesian optimization algorithm is combined
with adaptive Monte-Carlo sampling to optimize the yield of analog circuits and
static random-access memory (SRAM).
